Efficiently summarising relationships in large samples: a general duality between statistics of genealogies and genomes

### 2019-08-06 treestats_paper.tex
added new plots

\begin{figure}
    \includegraphics[width=0.5\textwidth]{{figures/1kg/relate_site_diversity_chr20}.png}
    \includegraphics[width=0.5\textwidth]{{figures/1kg/tsinfer_1kg_chr20.branch_diversity.2000000}.pdf}
    \includegraphics[width=0.5\textwidth]{{figures/1kg/tgp_geva_chr20.branch_diversity.2000000}.pdf}
    \includegraphics[width=0.5\textwidth]{{figures/1kg/relate_branch_diversity_chr20}.png}
    \caption{
        \textbf{(A)} Mean sequence diversity 
        in 500Kb \plr{?} windows along human chromosome 20 of the 1000 Genomes Project,
        and the dual branch statistic as calculated from tree sequences inferred by
        \textbf{(B)} tsinfer,
        \textbf{(C)} GEVA, and 
        \textbf{(D)} Relate.
        \label{fig:chr20}
    }
\end{figure}

>>>>

\begin{figure}
    \includegraphics[width=0.5\textwidth]{{figures/1kg/relate_chr20.site.1000000.diversity}.pdf}
    \includegraphics[width=0.5\textwidth]{{figures/1kg/1kg_chr20.branch.1000000.diversity}.pdf}
    \includegraphics[width=0.5\textwidth]{{figures/1kg/tgp_geva_chr20.branch.1000000.diversity}.pdf}
    \includegraphics[width=0.5\textwidth]{{figures/1kg/relate_chr20.branch.1000000.diversity}.pdf}
    \caption{
        \textbf{(top left)} Mean sequence diversity 
        in 1Mb windows along human chromosome 20 of the 1000 Genomes Project,
        and the dual branch statistic as calculated from tree sequences inferred by
        \textbf{(top right)} tsinfer,
        \textbf{(bottom left)} GEVA, and 
        \textbf{(bottom right)} Relate.
        \label{fig:chr20}
    }
\end{figure}
